---
title: "universal metadata"
output: html_document
---

We need a list of players names, dobs, and mlbids for matching.

We also need to have a general player lookup for optimal_auction that can be used to select players.  That should be a superset, containing every player in all the projection systems (and arguably all the prospects who might ever be drafted?)

First read in [Tanner's](http://www.smartfantasybaseball.com/tools/) amazing ID map:

```{r}

id_map_url <- 'https://docs.google.com/spreadsheets/d/1JgczhD5VDQ1EiXqVG-blttZcVwbZd5_Ne_mefUGwJnk'

#worked
id_map <- id_map_url %>%
  googlesheets::gs_url() %>%
  googlesheets::gs_read_listfeed()

head(id_map)

```

Presumably we'll manually add in some names here:

```{r}

#errata, manual additions...

```

Then save the id map as an .rda file so it can be used by the package:

```{r}

save(id_map, file = file.path('data', 'id_map.rda'))

```

errata: how to quickly make a minimal documentation file!
```{r, eval = FALSE}

paste0('\\item{', names(id_map), '}', '{', names(id_map), '}') -> foo
for (i in foo) {cat('#\' ');cat(i);cat('\n')}

```
